Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-08-11 tex/A.tex
Add a notice for Chapter 2
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Add a notice for Chapter 5 and fix typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\begin{document}
    \maketitle
    \begin{abstract}
        Argennon is a next generation cloud based blockchain and smart
        contract platform. The Argennon blockchain uses
        a hybrid proof of stake (HPoS) consensus protocol, which is capable of combining the benefits of
        a centralized and a decentralized system. In Argennon, ledger storage and transaction processing are
        outsourced to the cloud and normal personal computers or smartphones, with limited hardware
        capabilities, can validate transactions and actively
        participate in the Argennon consensus protocol. This property makes Argennon a truly decentralized and
        democratic blockchain and one of the most secure existing platforms.

@@

        The Argennon protocol strongly incentivizes the formation of a permission-less network of Publicly Verifiable
        Cloud (PVC) servers. A PVC server in Argennon, is a conventional data server which uses its computational and
        storage resources to help the Argennon network process transactions. This encourages the development
        of conventional networking, storage and compute hardware, which can benefit all areas of information technology.
        This contrasts with the approach of some older blockchains that incentivized the development of a totally
        useless technology of hash calculation.

@@

    \chapter{The Argennon Smart Contract Execution Environment}\label{ch:AVM}
    \input{sections/avm}

@@

    \chapter{The Argennon Blockchain}\label{ch:argennon-blockchain}

>>>>

\begin{document}
    \maketitle
    \begin{abstract}
        Argennon is a next generation cloud based blockchain and smart
        contract platform. The Argennon blockchain uses
        a hybrid proof of stake (HPoS) consensus protocol, which is capable of combining the benefits of
        a centralized and a decentralized system. In Argennon, ledger storage and transaction processing are
        outsourced to the cloud and normal personal computers or smartphones, with limited hardware
        capabilities, are able to validate transactions and actively
        participate in the Argennon consensus protocol. This property makes Argennon a truly decentralized and
        democratic blockchain and one of the most secure existing platforms.

@@

        The Argennon protocol strongly incentivizes the formation of a permission-less network of Publicly Verifiable
        Cloud (PVC) servers. A PVC server in Argennon, is a conventional data server which uses its computational and
        storage resources to help the Argennon network process transactions.

@@

    \chapter{The Argennon Smart Contract Execution Environment}\label{ch:AVM}
    \note{This chapter is outdated and does not include CI proofs. Currently a new version is being rewritten.}
    \input{sections/avm}

@@

    \chapter{The Argennon Blockchain}\label{ch:argennon-blockchain}
    \note{Currently a new version is being rewritten to include CI proofs.}
